Novel Generative Summaries: Safer Prompts & More insightful Market Research?

### 2024-06-21 writing/paper.qmd
pre-defense sync

---
author: Finn-Ole Höner (657110)
title: "working title"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \usepackage{tcolorbox}
  \usepackage{tikz}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 1in
            - bottom = 1in
            - left = 1in
            - right = 1in
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
---

@@

> *"Prompt engineering is the art of communicating eloquently to an AI."----Greg Brockman, President OpenAI*

<!-- TODO: Have more of an advertising claims example? -->
<!-- TODO: Make this more about a summary, than about generation and prompts? Build the bridge of the two -->
<!-- TODO: Talk about low-dim representation -->

Generative Large Language Models (LLM) are powerful, but unreliable tools for generating text. [A study by the NGO "Algorithm Watch"](https://algorithmwatch.ch/en/wp-content/uploads/2023/12/AlgorithmWatch_Generative-AI-and-elections_An-analysis-of-Microsofts-Bing-Chat.pdf), which is partially funded by the European Union, finds that Microsoft's chatbot Bing Chat, delivers wrong information in a third of its replies to election related questions, posing a risk to exacerbate desinformation.

Prompt engineering defines the task of finding the right prompt to generate a desired output. Typically, this is an interactive and iterative process between human and LLM. There are certain writing techniques that improve the quality of
the LLM's response, such as providing examples for what the desired output should look like. There are various [blog posts](https://huggingface.co/docs/transformers/en/tasks/prompting#best-practices-of-llm-prompting) and books [e.g. @phoenix2024prompt] about how to write good prompts, in fact businesses are [hiring "Prompt Engineers"](https://indeed.com/q-prompt-engineer-jobs.html?vjk=98ac28acfd1328d7) even on dedicated [job boards](https://prompt-engineering-jobs.com/jobs/prompt-engineer-qwvmju/). Despite these, supposedly low-barrier, resources, end users without AI knowledge still struggle with prompt engineering [@zamfirescu2023johnny]. Not only can prompt engineering pose a [security risk](https://www.promptingguide.ai/risks/adversarial), but the process is also fuzzy, hard to replicate, and might still lead to unpredictable behaviors of the model. These issues pose risks for organizations, as the obscurity of manual prompt engineering can lead to loss of know-how, and the unpredictiability of the model can lead to lawsuits, damages to brands, or missed opportunities.

Problems of reproduceability, transparency, and documentation, become critical for organizations with the advent of the [EU AI Act](https://digital-strategy.ec.europa.eu/en/policies/regulatory-framework-ai). The act requires for "High risk applications", that the AI model features, e.g. "adequate mitigation systems", "traceability of results", and, "robustness". High risk applications are not common and important for society, they include applications e.g. in education, employment, and public services.

We propose a new type of numeric document summary, which captures all the information contained in the document, as it can be used to recreate the document itself. This document summary comes in the form of a numeric vector, which we call the summary embedding. To obtain this summary embedding, we maximize the likelihood of generating the document with a Large Language Model (LLM). In this sense, these summary embeddings are optimal. We show, that these embeddings capture inherent information about the document, can be used for classification, and generation of new documents. There are only practical requirements for estimating these summary embeddings, namely that backpropagation of gradients is possible from the likelihood to the input of the LLM.

Beyond the methodological contribution, we show a marketing application of these summary embeddings and make a step towards using Generative AI in market research and design of the marketing-mix. We find that we can use these embeddings to capture design motivations of marketers behind advertising claims, and establish a measure for linguistic uniqueness of an advertising claim. Suprisingly, we find that this linguistic uniqueness is negatively correlated with the perceived uniqueness of an advertising claim by consumers. We explore these linguistic features and find that claims with certain words and their synonyms, cluster together, e.g. claims that emphasize the taste of a yoghurt drink or present it as a breakfast. Furthermore, we show that claims that live in certain areas of a low dimensional representation of the summary embeddings, are more likely to be rated favorably by consumers, but that small differences in wording can lead to relatively large differences in evaluation. This suggests a two-step approach to designing a market research study for advertising claims, where the first stage should focus on a wide exploration of the design space, while the second stage should focus on a fine-grained evaluation of the most promising area in this design space. We end with a sketch on how these summary embeddings can be used in an AI augmented design process, similar to applications in image data by @burnap2023product and @ludwigMachineLearningTool2023.

- Consumer preferences in latent generation space & Ad-claims
  - Market research is expensive. How can we leverage these insights better to improve its benefits?
  - What is missing from preference learning? How is this different?
    - Media products/things are different from products as attribute bundles
      - We can directly represent the product itself?
    - Brands and their role in advertising
  - We can view products as attribute bundles and get utilities for these attributes 
  - How do we do this for products that cannot be "discretized"?
  - Generative AI for personalization
    - Previously: Set pieces, e.g. recommendation systems
    - True personalization: Generate solution for each individual consumer
  - TODO: Add more product claim specific
  - Advertisements can be effective, @daiFrontiersWhichFirms2023a observe an increase in purchase intentions for restaurants that adapt online advertising by 7%-19%.
  - they are relevant @kongMadeUSAClaims2021
  - costs
  - need flexibility in online settings
  - closely related problems, such as email targeting @sahniPersonalizationEmailMarketing2018
  - advertising is one of the marketing-mix instruments which companies use to position themselves in the market and shapes the incentives of the system itself @moorthyTargetingAdvertisingSpending2023 @renAdvertisingContentCreation2023
  - design question
  - Ban of cookie-based advertising due to GDPR, adapting to observable behavior in live sessions or to context on the website itself becomes more important. GDPR
  - Challenges to cookies in website morphing
  - @beckerDoesItPay2019, point to the nuanced role that authenticity plays in advertising, especially with respect to its alignment with the brand and product. 
  - @edelmanBrandingDigitalAge2010 Concept of the consumer decision journey, product claims could vary across multiple visits or encounters of the same customer

@@

In the following, we compare our summary embeddings with three established methods to summarize documents: The Bidirectional Encoder Representations from Transformers (BERT) model's `[CLS]` token [@devlinBERTPretrainingDeep2018], pooled word embeddings [@shenBaselineNeedsMore2018], and prompt engineering approaches [@@huangenhanced].

The BERT model is a transformer [see @vaswani2017attention] based model to represent text. Its developers have pre-trained BERT on a large corpus of text, using two different self-supervised learning objectives. The first objective is the so called "Masked Language Model" task. Here, the researchers replace a random selection of tokens in the text by a mask token, and the goal of the BERT model is to predict which token is underlying this mask. In order to learn about the information captures in a sentence, the researchers also pose the "Next Sentence Prediction" task to the model. For this training objective, the BERT model receives a pair of two sentences and needs to predict whether the second sentence follows the first one in a text. This task trains the `[CLS]` token: As it is pre-pended before every such sentence pair, it learns a representation of the information contained in the focal sentence. In practice, the output for a `[CLS]` token serves as a powerful feature e.g. for sentence classification. BERT embeddings are versatile, but can also be fine-tuned to a specific task such as text summarization. However, such a fine-tuning requires the user to compile a dataset of text-summary and text pairs, that are representative of their application. These BERT representations are only descriptive and cannot be used for the generation of new text [see @devlinBERTPretrainingDeep2018]. There exist expansions to BERT, such as RoBERTa by @yinhanliuRoBERTaRobustlyOptimized2019, which improve the optimization procedure.

@shenBaselineNeedsMore2018 points to the value of using pooled word embeddings to represent documents. The idea behind a pooled word embedding is, that we can represent a sequence of tokens by aggregating the word-embeddings of these tokens. There are different methods we can use for this aggregation, some examples are the use of taking the average across the tokens (mean-pooling) or taking the maximum value across the tokens (max-pooling). There are various types of word embeddings that we could use for the pooling, often, these are non-attention word embeddings, such as Word2Vec [@tomasmikolovDistributedRepresentationsWords2013; @tomasmikolovEfficientEstimationWord2013] or Global Vectors (GLoVe) [@jeffreypenningtonGloveGlobalVectors2014]. These pooled word embeddings, cannot be used for text generation and perform worse than BERT embeddings in language tasks, as they do not employ the attention mechanism and loose information in the aggregation step [see e.g. @onanHierarchicalGraphbasedText2023].

We can also summarize documents by passing these to an LLM and prompting the model to write a summary for us [e.g. @huangenhanced; @chakrabortyAbstractiveSummarizationEvaluation2024]. However, these summaries are textual, not deterministic, and their quality depends on the formulation of the prompt. For example, @liuLostMiddleHow2023 find that answers of LLMs are better, when we place relevant information at the beginning or end of the prompt, while inserting emotions into prompts also improves the quality of the LLMs response, in some cases even doubling its performance [see @liLargeLanguageModels2023]. Another issue is that these summaries can vary in length, and one needs to specify how detailed a summary should be. The difference in length between the summary and focal document, also makes it challenging to evaluate how much of the information of the focal document is captured by the summary [@chakrabortyAbstractiveSummarizationEvaluation2024]. If these summaries are of a high quality, i.e. represent the information in the focal document well, then they can be useful when we want to share a written summary of a document. However, for many data science and automation tasks, we need a reliable numeric representation of the document, which is the focus of this paper.

In this work, we propose a method that optimizes the input prompt to an LLM, such that we obtain a desired outcome. We call these input prompts "document summaries", as the perfectly replicate a focal document. These input embeddings capture all information that is contained in a document, because we can re-generate the focal document just based on this summary embedding. These document summaries are deterministic, because we obtain them through maximum likelihood estimation and live in continuous space.  We can evaluate the fit of such a document summary, as the likelihood indicates its fit directly.

@@

| Method                              | Origin                                          | Reference                              |  Deterministic? |  Generation?  |  Type?  |
|:------------------------------------|:------------------------------------|:--------------------|:----------------------:|:----------------------:|:----------------------:|
| BERT `[CLS]` token                       | Next-sentence prediction task                  | @devlinBERTPretrainingDeep2018         | $\checkmark$   | $\times$       | Numeric    |
| Pooled Word Embeddings              | Aggregation of token information               | @shenBaselineNeedsMore2018             | $\checkmark$   | $\times$       | Numeric    |
| Prompt engineering                  | Emergent capability of LLM                     | CITE                                   | $\times$       | $\times$       | Textual    |
| Reverse engineered document summaries | Maximize the likelihood to re-generate the focal document | *Proposed method*                        | $\checkmark$   | $\checkmark$   | Numeric |
: Overview of existing methods to summarize documents. {#tbl-docsum}

@@

<!-- TODO: Normalization layer and its role; Does it work without it? Why / not? -->

Generative Large Language Models (LLM), such as [ChatGPT](https://chat.openai.com/) [@radford2018improving], generate text based on textual inputs, so called prompts. Internally, the model translates the prompt first into tokens, integer codes representing certain words, symbols and syllabuls, and then into a lower dimensional vector representation of the text itself, which we call the input embedding. This input embedding is then passed through a neural network that yields a probability distribution over the next token in the sequence. To generate text, the model makes a draw from this distribution, and attached this generated token at the end of the prompt, repeating this process until it predicts the next token to be the end-of-text token (eos), i.e. until it predicts that the text ends. LLMs are pre-trained on large text corpora, such as the [Common Crawl](https://commoncrawl.org/) which contains over 250 billion pages of text. Their architecture is rooted in the attention mechanism. The attention mechanism models interactions in the text, such as negations, synonyms, or grammatical structures, across a long sequence of text. @vaswani2017attention implement this mechanism in the transformer block, which is a modular building block for the neural network underlying an LLM. The combination of these transformer blocks, giant pre-training data, and huge computing resources, lead to LLMs that have "emergent capabilities". These are capabilities, which were not explicitly trained for by the developers of the model, such as the ability of a model to translate between languages, pass the BAR exam, or write textual summaries of documents [see @weiEmergentAbilitiesLarge; @luAreEmergentAbilities2023]. Unidirectional LLMs, such as GPT or LLaMa [@radford2018improving; @metaMetaLlama], are built for text-generation. They predict the next token in a sequence of tokens autoregressively, therby, these models only work from left-to-right (or right-to-left). Bidirectional LLMs, such as BERT [@devlinBERTPretrainingDeep2018], are built for representing text. They predict a token given the context around this token, and can hence read the text both from left-to-right and right-to-left. Both types of models share two note-worthy components, that account for a large share of their power. One, developers pre-train both types of models on large bodies of text, to learn about the structure of language itself. Two, by using a transformer architecture [@vaswani2017attention], which enables these language models to learn dependencies between words, such as negations (short-range dependency), or document structures, e.g. salutations in letters (long-range dependency). <!-- TODO: Simplify this paragraph -->

- For generation of sequences, the LLM autoregressively predicts the next token, given the previous tokens. At each step in the generation, a selection of the next token needs to take place, for which there exist various procedures (CITE). As we are optimizing with respect to the joint likelihood of the target sequence, we also need to generate with a procedure that generates this most likely sequence. Finding this sequence from the generation tree is a combinatorical problem and computationally not feasible. Hence, we use the beam-search heuristic to make our generation. Rather than only tracking the most likely token at each generation step, beam search also tracks the $n$-most likely tokens. The more beams we search, the more likely we are to find a sequence with a higher likelihood, then we would have found otherwise [@huggingfaceGenerateText].

Each document, in our case an advertising claim, $d$ consists of the tokens $t_1^{d}, \ldots, t_T^(d)$.

The probability to generate the sequence $t_1, \ldots, t_T$ with the LLM when using the embedding $\boldsymbol{s}$ as an input is $p(t_1, \ldots, t_T \mid \boldsymbol{s})$. We can split this probability into conditional probabilities due to the autoregressive architecture of the LLM and because we observe the target sequence. This provides large computational gains, as we can calculate these parts in parallel. Hence, we define the log-likelihood of the summary embedding for the target sequence as 
$$
\operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right) = \log p(t_1 | \boldsymbol{s}) + \log p(t_2 | t_1, \boldsymbol{s}) + \ldots + \log p(t_T | t_1, \ldots, t_{T-1}, \boldsymbol{s}) \text{, }
$$

and find the optimal summary embedding as

$$
\mathbf{s}^{*} = \argmax_{\boldsymbol{s}} \operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right) \text{. }
$$

We summarize the training process for the single summary embeddings in Algorithm 1. The summary embedding is a vector of length $E$, which is the same dimension as the dimension of the LLM's input embedding.

\begin{algorithm}
\begin{algorithmic}
\label{alg:singletraining}
\caption{Training of Single Summary Embeddings}
\State $i \gets 0$
\State $\epsilon \gets 0.01$
\State $\boldsymbol{s} \gets \operatorname{Initialization} \left( \cdot \right)$
\While{$True$}
    \State $l^{(i)} \gets \operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right)$
    \State $\nabla_{\boldsymbol{s}}^{(i)} l \gets \operatorname{ComputeGradient} \left ( l^{(i)}  \right )$
    \State $\boldsymbol{s}^{(i + 1)} l \gets \operatorname{Optimizer} \left(\boldsymbol{s}^{(i)}, \; \nabla_{\boldsymbol{s}}^{(i)} l \right)$
    \State $i \gets i + 1$    
    \If{$l^{(i)} < \epsilon$}
      \State \text{break}
    \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

As we are interested in finding a low-dimensional sub-space, in which we can represent the $D$ advertising claims, we use a factor model and estimate the summary embeddings for all advertising claims jointly, yielding the $D \times E$ matrix of summary embeddings $\mathbf{S}$. We restrict the degrees of freedom to $F$ hidden factors. To implement this factor model, we create an Autoencoder with one hidden layer, that is fully connected with linear activation functions [@goodfellowDeepLearning2016]. The input data to this autoencoder is an identity matrix of dimension $D$. We illustrate this neural network representation of the factor model in @fig-factor.

@@

thereby the matrix of summary embeddings for all claims becomes

@@

As as robustness check, we repeated this task for different attributes (instead of shiny, healthiness and colorfulness of hair), and for a different product category (surface cleaners). In total, we obtain 80 advertising claims, 20 for each of these settings. Half of these claims are supposed to be tangible and half intangible.

>>>>

---
author: Finn-Ole Höner (657110)
title: "Novel Generative Summaries: Safer Prompts & More insightful Market Research?"
date: last-modified
date-format: long
code-color-bg: lightgray
header-includes:
  \usepackage{fancyhdr}
  \usepackage{fancyvrb}
  \usepackage{float}
  \usepackage{booktabs}
  \usepackage{lscape}
  \usepackage{amsmath}
  \usepackage{graphicx}
  \usepackage{algorithm}
  \usepackage{algpseudocode}
  \usepackage{kpfonts}
  \usepackage{tcolorbox}
  \usepackage{tikz}
  \DeclareMathOperator*{\argmin}{arg\,min}
  \DeclareMathOperator*{\argmax}{arg\,max}
pdf-engine: pdflatex
format:
    pdf:
        documentclass: article
        toc: false
        number-sections: false
        number-depth: 2
        colorlinks: true
        fig-pos: 'H'
        fig-align: center
        geometry:
            - top = 1in
            - bottom = 1in
            - left = 1in
            - right = 1in
        papersize: dina4
bibliography: references.bib
echo: false
eval: true
messages: false
error: false
warning: false
cache: false
links-as-notes: true
---

@@

Many marketing problems in NLP require an accurate representation of the information contained in a text document. For example, we might want to analyze the design elements of advertising claims and predict their perception by consumers, or analyze the sentiment of a product review [@bergerUnitingTribesUsing2020a]. A powerful advance in NLP, are Large Language Models (LLM), such as GPT [@radford2018improving] and the demand of businesses for such tools is [growing rapidly](https://www.statista.com/outlook/tmo/artificial-intelligence/natural-language-processing/worldwide#market-size). In marketing, summarizing texts with these LLMs is becoming an important application [@hartmannNaturalLanguageProcessing2023]. However, using an LLM to summarize a document is difficult: The generated summaries depend on the wording of the used prompt and can be unreliable. Such textual summaries are also difficult to evaluate and are not practical to use in prevalent data science applications, such as prediction or clustering. In this work, we show how we can summarize documents with LLMs for this purpose.

<!-- TODO: Have more of an advertising claims example? -->
<!-- TODO: Make this more about a summary, than about generation and prompts? Build the bridge of the two -->
<!-- TODO: Talk about low-dim representation

A recent example of how prompts can lead to undesired behavior of the LLM is [a study by the European Union funded NGO "Algorithm Watch"](https://algorithmwatch.ch/en/wp-content/uploads/2023/12/AlgorithmWatch_Generative-AI-and-elections_An-analysis-of-Microsofts-Bing-Chat.pdf), which finds that Microsoft's chatbot Bing Chat delivers wrong information in a third of its replies to election related questions, exacerbating desinformation.
-->

A core distinction of our approach is, that we use an LLM to summarize a document without relying on prompt engineering. Prompt engineering defines the task of finding the right prompt to generate a desired output with a LLM. Typically, this is an interactive and iterative process between humans and LLM. Certain writing techniques improve the quality of the LLM's response, such as providing examples of what the desired output should look like. There are various [blog posts](https://huggingface.co/docs/transformers/en/tasks/prompting#best-practices-of-llm-prompting) and books [e.g. @phoenix2024prompt] about how to write good prompts. Businesses are [hiring "Prompt Engineers"](https://indeed.com/q-prompt-engineer-jobs.html?vjk=98ac28acfd1328d7) on dedicated [job boards](https://prompt-engineering-jobs.com/jobs/prompt-engineer-qwvmju/), indicating a demand for operating LLMs in a better way. Despite these, supposedly low-barrier, resources, end users without AI knowledge still struggle with prompt engineering [@zamfirescu2023johnny]. Not only can prompt engineering to pose a [security risk](https://www.promptingguide.ai/risks/adversarial), but the process is also fuzzy, hard to replicate, and might still lead to unpredictable behaviors of the LLM. These issues pose risks for organizations, as the obscurity of manual prompt engineering can lead to loss of know-how, and the unpredictability of the model can lead to lawsuits, damages to brands, and missed opportunities. Problems of reproducibility, transparency, and documentation become critical for organizations with the advent of the [EU AI Act](https://digital-strategy.ec.europa.eu/en/policies/regulatory-framework-ai). The act demands that the AI model features  "adequate mitigation systems", "traceability of results", and "robustness" when used for "High-risk applications". High-risk applications are common and important for society, as they include applications in education, employment, and public services. Hence, businesses and society alike have an interest in improving prompt engineering, in a way that makes the responses of LLMs better in quality and more robust.

To make prompt engineering more safe, we need to make an LLM's output more reliable. In this study, we make a step towards more reliable text generation by proposing a novel type of document summary, which we call the "generative summary". The core idea of our method is to find an input to the LLM that captures all the information contained in a focal document, as it leads the LLM to recreate this document itself. To obtain this summary, we maximize the likelihood of generating the document with a Large Language Model (LLM) given a numeric vector. Hence, these generative summaries are optimal. To mitigate overfitting and to make these embeddings more interpretable, we also introduce a factor model to estimate these document summaries in a lower dimensional space. We show that these embeddings capture inherent information about the document, and can be used for the generation of new documents. We also find that we can form linear combinations of generative summaries that have meaning themselves, similar to the approach by @mikolovDistributedRepresentationsWords2013 with word embeddings.

Furthermore, we illustrate the use of our generative summaries in a marketing setting and show how they can yield insights in market research. We apply our method to two datasets. First, an artificial dataset of advertising claims for hair shampoo and surface cleaners to validate that these generative summaries capture relevant information. Second, we show an application of these generative summaries in market research. We use these generative summaries to analyze market research data on product claims for a yogurt and a yogurt drink. We find that we can use these embeddings to capture the design elements of these claims, assess their linguistic uniqueness, and represent their design patterns. Surprisingly, we find that this linguistic uniqueness is negatively correlated with the perceived uniqueness of an advertising claim by consumers. We explore these linguistic features and find that claims with certain words and their synonyms cluster together, e.g. claims that emphasize the taste of a yogurt drink or present it as a breakfast. Furthermore, we show that claims that live in certain areas of a low dimensional representation of these summaries are more likely to be rated favorably by consumers, but that small differences in wording can lead to relatively large differences in evaluation. This suggests a two-step approach to designing a market research study for advertising claims, where the first stage should focus on a wide exploration of the design space, while the second stage should focus on a fine-grained evaluation of the most promising area in this design space. We end with a sketch of how managers can use these generative summaries to augment the design process and market research on product claims.

We proceed with a brief overview of the relevant literature and introduce our methodology. After testing our procedure on synthetic data, and exploring the low-dimensional factor space for the generation of new advertising claims, we apply our model to the market research data. We conclude with managerial implications, a discussion of the limitations of our approach and expansions for this research.

@@

<!-- TODO: Merge these paragraphs -->

In Natural Language Processing, words, symbols, and even syllables are represented by so-called tokens, integer codes representing a sequence of characters. A piece of text, represented by tokens, is what we call a document. To represent the meaning of words and phrases, rather than to just encode them by a token, we can use word embeddings. Word embeddings are numeric vectors that represent text. They are pre-trained on large amounts of text data and can capture the meaning of single words and phrases. Early approaches include the Word2Vec model by @mikolovDistributedRepresentationsWords2013. The researchers train these word embeddings through a model that predicts the text surrounding a focal word. Thereby they learn the context in which words occur, which is a way of representing their meaning. There are also approaches that create embeddings for sequences of words or even documents [e.g. @devlinBERTPretrainingDeep2018]. In this work, we use Large Language Models (LLMs). LLMs, such as [ChatGPT](https://chat.openai.com/) [@radford2018improving], predict the next word in a sequence of words. These models generate text based on textual inputs ("prompts"). Internally, the model translates these prompts into a sequence of vectors, the "input embedding". This input embedding is then passed through a neural network that predicts the next token in the sequence. To generate text, the model predicts the next token and attaches it to the prompt, repeating this process until it predicts the sequence to end (i.e. predicting the next token to be the "End-of-Sequence" token: "eos-token"). LLMs are pre-trained on large text corpora, such as the [Common Crawl](https://commoncrawl.org/) which contains over 250 billion pages of text. Their architecture is rooted in the attention mechanism. The attention mechanism models interactions in the text, such as negations, synonyms, or grammatical structures, as well as topics, across a long sequence of text. @vaswani2017attention implements this mechanism in the transformer block, which is a modular building block for the LLM. The combination of these transformer blocks, giant pre-training data, and huge computing resources lead to LLMs that have "emergent capabilities". These are capabilities, that were not explicitly trained for by the developers of the model, such as the ability of a model to translate between languages, pass the BAR exam, or write textual summaries of documents [see @weiEmergentAbilitiesLarge; @luAreEmergentAbilities2023].

In the following, we compare our *generative summaries* (*GS*) with three established methods to summarize documents:

- The Bidirectional Encoder Representations from Transformers (*BERT*) model's classifier token (CLS) [@devlinBERTPretrainingDeep2018]
- Pooled word embeddings (*PWE*)  [@shenBaselineNeedsMore2018] 
- Prompt engineering approaches (*PE*) [@huangenhanced; @khattabDSPyCompilingDeclarative2023]

<!-- TODO: Start with word embeddings themselves 
Word embeddings are numeric vectors that represent text.
-->

__BERT__: An advanced approach to estimate a word embedding is the *BERT* model, which is a transformer-based model to represent text [see @vaswani2017attention]. Its developers have pre-trained BERT on a large corpus of text, using two different self-supervised learning objectives. The first objective is the so-called "Masked Language Model" task. Here, the researchers hide a random token in a sequence, and the goal of the BERT model is to predict which token is missing. This teaches the model the meaning of words in context. To learn about the information captured in a sentence, the researchers also pose the "Next Sentence Prediction" task to the model. For this training objective, the BERT model receives a pair of two sentences and needs to predict whether the second sentence follows the first one in a text. This task trains the classifier token (CLS): As it is pre-pended before every such sentence pair, it learns a representation of the information contained in the focal sentence. In practice, the output for a CLS token serves as a powerful feature e.g. for sentence classification. BERT embeddings are versatile, but can also be fine-tuned to a specific task such as text summarization. Such a fine-tuning requires the user to compile a dataset of summary-text pairs, that are representative of their application. These BERT representations are only descriptive and cannot be used for the generation of new text [see @devlinBERTPretrainingDeep2018]. In contrast to generative LLMs, such as GPT [@radford2018improving], which consider context only unidirectional, BERT takes text from the left and the right into account when representing it as an embedding. There exist improvements to BERT, such as RoBERTa by @yinhanliuRoBERTaRobustlyOptimized2019, which improve the optimization procedure.

__PWE__: @shenBaselineNeedsMore2018 argues that pooled word embeddings (*PWE*) are a simple, yet powerful way to represent documents. The idea behind a *PWE* is that we can represent a sequence of tokens by aggregating the word embeddings of these tokens. There are different methods we can use for this aggregation, such as taking the average across the tokens (mean-pooling) or taking the maximum value across the tokens (max-pooling). There are various types of word embeddings that we could use for the pooling, such as Word2Vec [@mikolovDistributedRepresentationsWords2013; @mikolovEfficientEstimationWord2013] or Global Vectors (GLoVe) [@jeffreypenningtonGloveGlobalVectors2014]. These pooled word embeddings, cannot be used for text generation and perform worse than BERT embeddings in language tasks, as they do not employ the attention mechanism and lose information in the aggregation step [see e.g. @onanHierarchicalGraphbasedText2023].

__PE__: We can also summarize documents by passing these to an LLM and prompting the model to write a summary for us (Prompt engineering approaches, *PE*) [e.g. @huangenhanced; @chakrabortyAbstractiveSummarizationEvaluation2024]. However, these summaries are textual, not deterministic, and their quality depends on the formulation of the prompt. For example, LLMs deliver better answers when the prompt contains relevant information at the beginning or the end, or when the prompt is written emotionally [see @liuLostMiddleHow2023; @liLargeLanguageModels2023]. Another issue is that these summaries can vary in length, and one needs to specify how detailed a summary should be. The difference in length between the summary and focal document, also makes it challenging to evaluate how much of the information of the focal document is captured by the summary [@chakrabortyAbstractiveSummarizationEvaluation2024]. If these summaries are of a high quality, i.e. represent the information in the focal document well, then they can be useful when we want to share a written summary of a document. In this paper, we propose a solution that works for data science and automation tasks, as we create a numeric representation of the document. We could use these textual summaries for generation, in the sense that we could prompt the model to generate a new document based on the summary.

A recent improvement to *PE* approaches is the framework proposed by @khattabDSPyCompilingDeclarative2023. This framework, called "Declarative Self-improving Language Programs, pythonically" (DSPy), learns how to combine different prompting and finetuning techniques to improve the generated answer. They show that their discrete optimization leads to better output compared to expert-designed prompts, even when applied to smaller LLMs. Their approach is text-based and revolves around generating examples of the desired output and then tuning the prompt and the LLM itself based on these examples. In spirit, their approach is similar to hyper-parameter tuning, in that it uses a type of (small) training data and a performance metric (e.g. whether the answer is an exact match to a certain label), and then adjusts the prompt and the LLM to maximize the scoring of its answer on this training set. The twist is, that the DSPy framework can perform such hyper-parameter tuning in an automized fashion, by generating candidate prompts itself and selecting from them. Our proposed approach differs from DSPy in that we optimize in a continuous space, and that our goal is to find a numeric summary for a document, rather than to generate a good response to language tasks, such as question answering.

__GS__: In this work, we propose *generative summaries* (GS) which optimize the input prompt to an LLM, such that we obtain a desired outcome. These *generative summaries* should perfectly replicate the document they summarize, thereby capturing all information contained in it. These document summaries are deterministic because we obtain them through maximum likelihood estimation and they live in continuous numeric space. We can evaluate the quality of such a document summary directly through the obtained likelihood.

@@

| Method                              | Origin                                          | Reference                              |  Deterministic? |  Generation?  |  Type?  |
|:---------|:------------------------------------|:--------------------|:---------------:|:---------------:|:--------------------:|
| *BERT*                       | Next-sentence prediction task                  | \footnotesize @devlinBERTPretrainingDeep2018         | $\checkmark$   | $\times$       | Numeric    |
| *PWE*              | Aggregation of token information               | \footnotesize @shenBaselineNeedsMore2018             | $\checkmark$   | $\times$       | Numeric    |
| *PE*                  | Emergent capability of LLM                     | \footnotesize @khattabDSPyCompilingDeclarative2023                                   | $\times$       | $\checkmark$       | Textual    |
|                   |                      |  |        |        |     |
|                   |                      |  |        |        |     |
| __*GS*__ | Maximize the likelihood to regenerate the focal document | __*Proposed method*__                        | $\checkmark$   | $\checkmark$   | Numeric |
: Overview of methods to summarize documents. {#tbl-docsum}

To validate whether our proposed approach is a viable alternative to these established methods, we will evaluate three aspects of our generative summaries on an artificial dataset, and explore their use in marketing applications. This yields these three *research objectives* for the validation and one explorative objective for the marketing application:

1) Can we use these generative summaries for classification tasks?
2) Can we regenerate the summarized document with our generative summaries?
3) Can we generate new documents based on our generative summaries?
4) *Explorative*: Can these generative summaries deliver useful insights in market research?

@@

<!-- TODO: Normalization layer and its role; Does it work without it? Why / not? -->
<!--

- For generation of sequences, the LLM autoregressively predicts the next token, given the previous tokens. At each step in the generation, a selection of the next token needs to take place, for which there exist various procedures (CITE). As we are optimizing with respect to the joint likelihood of the target sequence, we also need to generate with a procedure that generates this most likely sequence. Finding this sequence from the generation tree is a combinatorical problem and computationally not feasible. Hence, we use the beam-search heuristic to make our generation. Rather than only tracking the most likely token at each generation step, beam search also tracks the $n$-most likely tokens. The more beams we search, the more likely we are to find a sequence with a higher likelihood, then we would have found otherwise [@huggingfaceGenerateText].
  -->

<!-- Each document, in our case an advertising claim, $d$ consists of the tokens $t_1^{d}, \ldots, t_T^{(d)}$. -->

The probability of generating the sequence $t_1, \ldots, t_T$ with the LLM when using the embedding $\boldsymbol{s}$ as an input is $p(t_1, \ldots, t_T \mid \boldsymbol{s})$. We can split this probability into conditional probabilities due to the autoregressive architecture of the LLM and because we observe the target sequence. This provides large computational gains, as we can calculate these parts in parallel. Hence, we define the log-likelihood of the generative summary for the target sequence as 
$$
\operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right) = \log p(t_1 | \boldsymbol{s}) + \log p(t_2 | t_1, \boldsymbol{s}) + \ldots + \log p(t_T | t_1, \ldots, t_{T-1}, \boldsymbol{s}) \text{, }
$$

and find the optimal generative summary as

$$
\mathbf{s}^{*} = \argmax_{\boldsymbol{s}} \operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right) \text{. }
$${#eq-single}

We summarize the training process for these single generative summaries in Algorithm 1. The generative summary is a vector of length $E$, which is the same dimension as the LLM's input embedding.

\begin{algorithm}[H]
\begin{algorithmic}
\label{alg:singletraining}
\caption{Training of Single Summary Embeddings}
\State $i \gets 0$
\State $\epsilon \gets 0.01$
\State $\boldsymbol{s} \gets \operatorname{Initialization} \left( \cdot \right)$
\While{$True$}
    \State $l^{(i)} \gets \operatorname{\mathcal{L}} \left ( \boldsymbol{s} \mid t_1, \ldots, t_T \right)$
    \State $\nabla_{\boldsymbol{s}}^{(i)} l \gets \operatorname{ComputeGradient} \left ( l^{(i)}  \right )$
    \State $\boldsymbol{s}^{(i + 1)} \gets \operatorname{Optimizer} \left(\boldsymbol{s}^{(i)}, \; \nabla_{\boldsymbol{s}}^{(i)} l \right)$
    \State $i \gets i + 1$    
    \If{$l^{(i)} < \epsilon$}
      \State \text{break}
    \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

To regularize these embeddings and make them more interpretable, we are interested in finding a low-dimensional sub-space in which we can represent the $D$ advertising claims. For this, we use a factor model and estimate the generative summaries for all advertising claims jointly, yielding the $D \times E$ matrix of generative summaries $\mathbf{S}$. We restrict the degrees of freedom to $F$ hidden factors. To implement this factor model, we create an autoencoder with one hidden layer that is fully connected with linear activation functions [@goodfellowDeepLearning2016]. The input data to this autoencoder is an identity matrix of dimension $D$, making it a factor model. Before passing the generative summary to the LLM, we normalize them with layer normalization [@baLayerNormalization2016]. Layer normalization works across the hidden nodes, rather than across the observations in a batch [batch-normalization, see @ioffeBatchNormalizationAccelerating2015]. Thereby, it can also be used with a single observation. In the optimization, we encounter sharp spikes in our gradients, that originate in the decoder of the model. We mitigate these by gradient clipping [@zhangWhyGradientClipping2020].  We illustrate this neural network representation of the factor model in @fig-factor.

@@

thereby the matrix of generative summaries for all claims becomes

@@

: Tangible (T) and Intangible (I) advertising claims for hair shampoo products. (Created by ChatGPT) {#tbl-claims}
